\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}	


%\chapter*{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \bf Acknowledgments}
\end{center}

\vspace{1cm}

\begin{center}
    To my family
\vspace{1cm}
\end{center}

% M.K.
% L.C.G.
% D.P.
% H.M.A.
% G.A.
% C.S.
% T.R.
% A.S.
% E.R.
% V.R.
% M.C.B.

\vspace{1cm}


My family has patiently supported me during this four-month quest in science and
technology. My appreciation to my equally dear, and loyal friends. Thanks to
Dejan Pangercic, my advisor, who was the first to introduce me into the
challenges to be found in the world of robotics and computer vision. Lucian
Goron was never short of pragmatic advice. Thumbs up for Manuel Baierl for
finding a money- and time-saving shortcut to the laboratory. The discussions
with Martin Kreuzeder helped to shape my understanding about geometry, proving
useful in several parts of this work.  Many thanks to Hans-Martin Adorf for his
generous comments, and his advice on style.  Thanks to Gabriel Adorf and
Christian Schöne, who both taught me about the importance of graphics, and the
basics in how to create them. Yet, my drawings are no match for their's. Thanks
to Chanrith Siv for helping me to remove the roughest edges in my English
writing.  Thanks to Alexander Shishkov, Ethan Rublee, and Vincent Rabaud for
their comments on software that was not supposed to be used by the public. I am
grateful for the help of Zoltan-Csaba Marton and Thomas Rühr, who helped me
operating the robot at Technische Universität München. Thank you.

