%\chapter{Introduction}
%\label{chapter:introduction}

\section{Intended Purpose}

Recognition of objects is a fundamental problem in computer vision. We present
a system that detects a textured object and finds its pose in a cluttered
scene. A cluttered scene is formed by multiple textured objects that often
partially occlude each other and are only partially visible to the observer.
The intended purpose of this system is to allow a robot to find the pose of an
object pose such that a robot can then resolve the clutter by scene
manipulation. We assume that objects are removed by the robot from the scene
one-by-one, thus our system focuses on robustly finding the pose of a single
object rather than attempting to recognize all objects in the cluttered scene
at once.

The challenges of solving such a task are plenty. Partial occlusion renders the 
task of detecting objects difficult. The objects in the cluttered scene might
be arbitrarily rotated, and we cannot make any prior assumption about their
principal axes.

A possible application of the system is in household environments, such as a
kitchen.  Let us assume that a robot is given the task to go shopping and that
it will empty the shopping bag onto a kitchen table. Cans, bottles and boxes
and many other items from supermarkets are all textured objects. The next step
for the robot is to move all shopping items to appropriate locations in the
kitchen. The shopping items are assumed to be textured objects and they form a
cluttered scene on the kitchen table. Our system will then provide the robot
with sufficient information to remove one of the items from the cluttered
scene. Multiple iterations will allow the robot to fully resolve the scene.

The actual manipulation of the scene by a robot is not part of this work, but
the application provides the constraints and the assumptions of our system. A
textured object shall be recognized with high and measurable confidence, and
also be correctly located within tolerable error bounds.

\section{Related Work}

... xyz did that ... z means this is difficult ... a chose this .. b did something
similar but based on different assumptions ... 

\section{Selected Approach}

Our approach is based on constructing 3d models and extracting local 2d
features from template objects. Local features have significant advantage over
template matching when objects are partially occluded. % TODO: citation Every
Given a query image, we then match local 2d features to obtain a mapping
between 2d keypoints that belong to the query image and 3d points from the
previously learned template model. We then generate estimates for the object
poses on the query image based on Random Sample Consensus (RANSAC). The pose
that is supported by the highest number of matches is then refined by a second
cascaded classifier that has only been trained on the single object. Each
estimate is assigned a confidence probability that has been learned on ground
truth data. In case the ground truth data is sufficiently similar to the data
encountered in applications, this confidence probability might be used for
selecting a trade-off between true and false positive rates.% TODO: Zitat Fawcett 2006

